Summary of PM2.5 Nonattainment  Analysis

### 2020-11-09 Analysis Files/Paper_Analysis_327.Rmd
tiny changes

### Basic Data Description (Section 2.2)
```{r,  echo=FALSE}
print(paste("Total number of locations =", dim(dat)[[1]]))
print(paste("Total number of fee-for-service Medicare beneficiaries =", sum(dat$Total_den_FFS.2012)))
print(paste("Total number of managed care Medicare beneficiaries =", sum(dat$Tot_den_for_death_MA_FFS.2012) - sum(dat$Total_den_FFS.2012)))
```
### Nonattainment Description (Section 2.2)
```{echo=FALSE}
print(paste("Number of nonattainment areas =", sum(dat$a==1)))
print(paste("Number of nattainment areas =", sum(dat$a==0)))

>>>>

### Basic Data Description (Section 2.2)
```{r,  echo=FALSE}
print(paste("Total number of locations =", dim(dat)[[1]]))
print(paste("Total number of fee-for-service Medicare beneficiaries =", sum(dat$Total_den_FFS.2012)))
print(paste("Total number of managed care Medicare beneficiaries =", sum(dat$Tot_den_for_death_MA_FFS.2012) - sum(dat$Total_den_FFS.2012)))
```
### Nonattainment Description (Section 2.2)
```{r, echo=FALSE}
print(paste("Number of nonattainment areas =", sum(dat$a==1)))
print(paste("Number of nattainment areas =", sum(dat$a==0)))
